Outstanding Title

### 2017-04-26 writing/EpiDraft.Rmd
Run checks for correct location
Adjusting Leg simulation

@@

```{r, echo=F}
#Question: does exposure need to have trend or is it enough to just make outcome look like real data?
exposure <- continuous_exposure(n=1001, mu = 65, sd = 3, trend = "no trend", amp=.4)
#Make this into weekly data instead of daily.
exposuremat <- matrix(data=exposure$x, ncol = 7, nrow=143, byrow=T)
exposurex <- apply(exposuremat, 1, mean)
newdate <- seq.int(from=exposure$date[1], to=exposure$date[1001], by=7)
weeklyexp <- data.frame(date=newdate, x=exposurex)
plot(weeklyexp, main = "Plot of Exposure values")
outcome <- sim_outcome(weeklyexp, average_outcome = 10, trend = "cos1linear")
plot(outcome$outcome)

#Try with eesim function
leg <- eesim(n_reps=1, n=800, central = 65, sd = 3, exposure_type = "continuous", exposure_trend = "no trend", exposure_amp=.6,average_outcome = 10, outcome_trend = "cos1linear", outcome_amp = .6, rr= 1.02, model = "spline", df_year = 4)
plot(leg[[3]]$outcome)
```

>>>>

```{r}
#Checking for anomalies:
leg_cases[which(leg_cases$checkma != "MID. ATLANTIC"),]
leg_cases[which(leg_cases$checknyc != "N.Y. City"),]
leg_cases[which(leg_cases$checkpa != "Pa."),]

#Row 48 is the only row with different states. 569 and 574 have NA in every column.
```

@@

```{r, echo=F}
#Means of real data:
map(leg_cases[,2:4], mean, na.rm=T)
#(ma=14.633, nyc=4.69, pa=5.314)
exposure <- continuous_exposure(n=1001, mu = 65, sd = 5, trend = "cos1", amp=.4)
#Make this into weekly data instead of daily.
x <- seq.int(from=1, to=1001, by=7)
weeklyexp <- exposure[x,]
plot(weeklyexp, main = "Plot of Exposure values")
outcome <- sim_outcome(weeklyexp, average_outcome = 4.69, trend = "no trend")
plot(outcome$outcome)
